SpecHunter: Interactively Inferring Taint Specifications Using Bayes Net

### 2021-04-03 My-Papers/SpecHunter/paper.tex
checkpoint

\usepackage{listing}

@@

\subsection{Network Construction}

% Network Construction은 반드시 Scalability and Efficiency와 연관되게 되어 있다.
% 그 점을 유념하면서 쓰자: 적절한 pointer 달아 주기.
Here we describe how we represent the input java project into a graph form, which will
later be turned into a series of Bayesian networks. We hope to create a graph G=(V, E),
where V is the set of all methods used or defined in the given application, and E is a
subset of V * V, whose elements are gathered in three different ways.

First, there are data-flow-edges. We perform a variant of a data-flow analysis on the
given input application to calculate lifetimes of all access paths found in the entire code.
% 여기서 간단한 예제 넣어주기

\begin{figure}[t]
  \begin{lstlisting}

    public int m1() {
      return 1;
    }

    public int m2(int u1) {
      return ++u1;
    }

    public void m3(int u2) {
      System.out.println(u2);
    }

    public void f() {
      int x = m1();
      g(x);
    }

    public void g(int y) {
      int z = m2(y);
      h(z);
    }

    public void h(int w) {
      m3(w);
    }

  \end{lstlisting}
\caption{Example Java program with a data flow.}
vspace{-0.6em}
\label{fig:sca}
\end{figure}

Second, there are call-edges.

Last but not least, there are similarity-edges.

\subsection{Graph Splitting}

\subsection{Information Propagation}

@@

\paragraph{Threats to Validity.}

>>>>

\usepackage{listings}

\lstset{
  language=Java,
  numbers=left,
  stepnumber=1,
  firstnumber=1,
  numberfirstline=true
}

@@

\subsubsection{Network Construction}

\paragraph{Determining Edges}

% Network Construction은 반드시 Scalability and Efficiency와 연관되게 되어 있다.
% 그 점을 유념하면서 쓰자: 적절한 pointer 달아 주기.
Here we describe how we represent the input java project into a large graph form, which will
later be turned into a series of Bayesian networks. How we splitt this large
graph into several Bayesian networks will be discussed in the next section. % TODO 좀 더 자연스러운 포인터??
We hope to create a graph $G=(V, E)$,
where $V$ is the set of all methods used or defined in the given application, and $E$ is a
subset of $V\times V$, whose elements are gathered in three different ways.

First, there are data-flow-edges. We perform a variant of a data-flow analysis on the
given input application to calculate lifetimes of all access paths found in the
entire codes, starting from being defined and ending by being ``dead'', between
which the access path may be ``redefined''.
% 여기서 간단한 예제 넣어주기

\lstinputlisting[language=Java]{./Codes/SimpleExample.java}

In the above example, a variable \texttt{x} is being defined to hold the value \texttt{1} in the method
\texttt{f}, using another method \texttt{m1}. This value flows to \texttt{g}, where this
value is redefined as \texttt{2} using the method \texttt{m2}. After this redefined
value flows to method \texttt{m3} via \texttt{h}, it is no longer used after the call to
\texttt{println}. Here, our goal is to capture this lifecycle. To compute these
for all access paths in the program, we first run a static analysis designed as follows:

% 무슨 environment를 써야 하나...? 일단 적어보쟈

\begin{align*}
  A\in \mathbb{D} = \mathbb{C}\rightarrow\mathcal{P}(State)\\
  s\in State = Procname\times Var\times Loc\times Alias\\
  p\in Procname \subseteq Var\\
  a\in Alias \subseteq \mathcal{P}(Var)
\end{align*}

For example, for an assignment statement \texttt{int a = b;} inside a procedure
\texttt{f} at line 3, we obtain the tuple set \texttt{\{(f, a, 3, \{a, b\})\}}.
The fourth component of the tuple means that \texttt{a} and \texttt{b} are
aliases. After we create such tuples for each program point, we finally construct
\emph{propagation chains} by threading the tuples via alias relations. The
relevant generated tuples for our goal is:

\begin{itemize}

\item \texttt{\{(f, x, 14, \{x, y\})\}}
\item \texttt{\{(g, y, 18, \{y, u1\})\}}
\item \texttt{\{(m2, u1, 5, \{u1\})\}}
\item \texttt{\{(m2, u1, 6, \{u1\})\}}
\item \texttt{\{(g, z, 6, \{z, u1, w\})\}}
\item \texttt{\{(g, w, 23, \{w, u2\})\}}
\item \texttt{\{(m3, u2, 9, \{u2, println_1\})\}}

\end{itemize}

where \texttt{println_1} is a Mangled parameter variable of \texttt{println}.
Now, connecting the tuples with the aliases, we get two chains: \texttt{x -> y
  -> u1} and \texttt{u1 -> z -> w -> u2 -> println_1}. Since \texttt{u1} is
redefined in \texttt{m2}, we glue the two together to get the originally desired
information: \texttt{x -> y -> u1 -> z -> w -> u2 -> println_1}. This translates
into data-flow edges: \texttt{(f, g)}, \texttt{(f, h)}, and \texttt{(m3, println)}.

% 아 이거 실제로 돌려봐서 확인해야 할 거 같은뎅.. 실제로 이렇게 나오나...?

% TODO static callee가 무엇인지를 좀 알아와서 디테일을 추가할 것.
Second, there are call-edges. Since we used Facebook's Infer (fbinfer.com/) to
implement our static analysis, we used Infer's facility to compute static
callees of a given method to draw the entire callgraph of a given application
code. For each caller \texttt{f} and its callee \texttt{g}, we add an edge
\texttt{(f, g)}.

Last but not least, there are similarity-edges. The idea is to take any two
methods and score its pairwise similarity, and leave only the pairs with score
above a predefined threshold.
% TODO syntactic, semantic feature 표 넣기

\paragraph{Determining CPTs}

% 여기서는 표를 좀 빡시게 그려야 한다. 셀도 좀 색칠하고...

\subsubsection{Graph Splitting}

\subsubsection{Information Propagation}

@@

\paragraph{Threats to Validity}
